---
title: "mytinyshinys - Sports Blog"
author: "mytinyshinys"
date: "March 5, 2016"
output:
  html_document:
    fig_caption: yes
    theme: journal
    toc: true
    toc_depth: 2
    code_folding: hide
css: customBlog.css
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
```

```{r libraries, echo=TRUE, include= FALSE}
# # libraries required
library(shiny)
library(shinydashboard)
library(stattleshipR)
library(dplyr)
library(readr)
library(stringr)
library(plotly)

```
This is a series of short articles usually related to apps I develop for the [mytinyshinys site](https://mytinyshinys.shinyapps.io/dashboard/) focusing on non-soccer Sports.
Commented out code can be shown or hidden by toggling buttons

##  <span class="post">NBA - Gamelogs</span>
*18th March 2016*


A [recent article](http://blog.stattleship.com/will-steph-curry-hit-272-threes-before-reaching-600-attempts/?utm_content=buffer8d469&utm_medium=social&utm_source=twitter.com&utm_campaign=buffer).
by [Mara Averick](https://twitter.com/dataandme) on Stephen Curry's record breaking three-point season prompted me to replicate one of her examples for a shiny app

The data comes from the [Stattleship API](https://www.stattleship.com/)  which seems a great addition for sports data junkies. But get in fast as they will be charging soon!

You will need to obtain your own token from Stattleship if you wish to copy and use code


```{r 160318 data loading, echo=TRUE}

teams <- read_csv("https://dl.dropboxusercontent.com/u/25945599/nbaTeams.csv")
players <- read_csv("https://dl.dropboxusercontent.com/u/25945599/nbaPlayers.csv")

players <- players %>% 
  arrange(name)

playerChoice <- players$slug
names(playerChoice) <- players$name

## enter own token if copying code
#token <-set_token(<enter your token>)

## set params
sport <- "basketball" 
league <- "nba"

```
```{r Stattleship token, echo=FALSE}
token <-set_token('14954863fc861a855e8510512308dd38')

```


I have made some slight changes to Mara's code but, hopefully, the end product is the same. The key ss_get_result function is from the stattleshipR package    
A selection can be made from all NBA players who have appeared so far in the 2015/6 season    
Click button to create chart which will be based on current data

```{r 160318 processing, echo=TRUE}


## set inputs
inputPanel(
selectInput("player", label=NULL,playerChoice, selected="nba-stephen-curry"),
      radioButtons("category", label=NULL, choices=c("FG","3P","FT"),inline=T),
      actionButton("go","Get Player Data")
)

# processing based on input
data <-eventReactive(input$go,{
  
  req(input$player)
  name <- players[players$slug==input$player,]$name
  
  ep <- "game_logs"    
  q_body <- list(player_id=input$player)
  

  nba <- ss_get_result(token=token,sport=sport, league=league, ep=ep, query=q_body, version=1, verbose=TRUE, walk=TRUE)
  logs <- lapply(nba, function(x) x$game_logs)
  games <- lapply(nba, function(x) x$games)
  
  
  games_df <- tbl_df(rbindlist(games)) 
  logs_df <- rbindlist(logs)

  logs_df <- logs_df %>% 
    filter(game_played == "TRUE")
  
  logs_df[is.na(logs_df )] <- 0
  logs_df$court <- ifelse(logs_df$team_outcome == logs_df$home_team_outcome, "home", "away")
  
  # joining data.frames - alternative methods are available
  logs_df$scoreline <- games_df[match(logs_df$game_id, games_df$id),]$scoreline
  logs_df$winning_team_id <- games_df[match(logs_df$game_id, games_df$id),]$winning_team_id
  logs_df$score_differential <- games_df[match(logs_df$game_id, games_df$id),]$score_differential
  logs_df$game_started_at <- games_df[match(logs_df$game_id, games_df$id),]$started_at
  logs_df$game_ended_at <- games_df[match(logs_df$game_id, games_df$id),]$ended_at
  logs_df$game_slug <- games_df[match(logs_df$game_id, games_df$id),]$slug
  
  # ensuring data is chronologically correct
 logs_df <- logs_df %>% 
   arrange(game_ended_at)
  
  info=list(logs=logs_df,games=games_df,player=name)
  return(info)
  
})

## create  and output chart
renderPlotly({
  
  # simplify code
  df <- data()$logs

  
 # create basic chart based on category
  if (input$category=="3P") {
p <-  pc <- round(100*sum(df$three_pointers_made)/sum(df$three_pointers_attempted),1)
  theTitle <- paste0(data()$player, " - 3 Pointers ",pc,"%")
  
  plot_ly(data()$logs, x = cumsum(three_pointers_attempted), y = cumsum(three_pointers_made), mode = "markers", hoverinfo = "text", group=team_outcome, 
          text = paste(str_sub(game_started_at,1,10),"<br> Made:",three_pointers_made,"<br> Attempts:",three_pointers_attempted,"<br> Tot Made:",cumsum(three_pointers_made),"<br> Tot Attempts:",cumsum(three_pointers_attempted)))
  } else if (input$category=="FG") {
    p <-  pc <- round(100*sum(df$field_goals_made)/sum(df$field_goals_attempted),1)
    theTitle <- paste0(data()$player, " - Field Goals ",pc,"%")
    
    plot_ly(data()$logs, x = cumsum(field_goals_attempted), y = cumsum(field_goals_made), mode = "markers", hoverinfo = "text", group=team_outcome, 
            text = paste(str_sub(game_started_at,1,10),"<br> Made:",field_goals_made,"<br> Attempts:",field_goals_attempted,"<br> Tot Made:",cumsum(field_goals_made),"<br> Tot Attempts:",cumsum(field_goals_attempted)))
  } else if (input$category=="FT") {
    p <-  pc <- round(100*sum(df$free_throws_made)/sum(df$free_throws_attempted),1)
    theTitle <- paste0(data()$player, " - Free Throws ",pc,"%")
    
    plot_ly(data()$logs, x = cumsum(free_throws_attempted), y = cumsum(free_throws_made), mode = "markers", hoverinfo = "text", group=team_outcome, 
            text = paste(str_sub(game_started_at,1,10),"<br> Made:",free_throws_made,"<br> Attempts:",free_throws_attempted,"<br> Tot Made:",cumsum(free_throws_made),"<br> Tot Attempts:",cumsum(free_throws_attempted)))
  }
  # Then add layout
  p %>%  
    layout(hovermode = "closest",
           xaxis=list(title="Cumulative Attempts"),
           yaxis=list(title="Cumulative Made"),
            title= theTitle, titlefont=list(size=16)
           
    ) %>% 
    # hide plotly options
    config(displayModeBar = F)
  
})

```


###  <span class="blogs">myTinyShiny blogs</span>


- [English Premier League](https://mytinyshinys.shinyapps.io/premierBlog)
- [Other Sports](https://mytinyshinys.shinyapps.io/sportsBlog)
- [Socio-Economic](https://mytinyshinys.shinyapps.io/socioEconomicsBlog)
- [Analytics](https://mytinyshinys.shinyapps.io/analyticsBlog)


###  <span class="blogs">Associated mytinyshiny web sites</span>


- [Cricket](https://mytinyshinys.shinyapps.io/cricket)
- [MLB](https://mytinyshinys.shinyapps.io/mlbCharts)
- [NBA](https://mytinyshinys.shinyapps.io/nbaCharts)